Plots and tables summarizing results of Poisson simulations

### 2020-06-23 analysis/gaussmeanest.Rmd
A few small revisions to the workflowr analyses.

Now, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line) for one simulated dataset as an illustration

>>>>

Now, we plot the ground-truth signal (the mean function, drawn as a
black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line) for one simulated dataset as an
illustration.

### 2020-06-23 analysis/poisson.Rmd
A few small revisions to the workflowr analyses.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
```

@@

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x    <- rpois(n,mu.s)
create.signal.plot(t,x,mu.s)
```

@@

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x      <- rpois(n,mu.ang)
create.signal.plot(t,x,mu.ang)
```

@@

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x     <- rpois(n,mu.hs)
create.signal.plot(t,x,mu.hs)
```

@@

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x      <- rpois(n,mu.bur)
create.signal.plot(t,x,mu.bur)
```

@@

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(t,x,mu.cb)
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(t,x,mu.b)
```

@@

pdat <- rbind(pdat.s1,pdat.s8,pdat.s128,
              pdat.ang1,pdat.ang8,pdat.ang128,
              pdat.hs1,pdat.hs8,pdat.hs128,
              pdat.bur1,pdat.bur8,pdat.bur128,
              pdat.cb1,pdat.cb8,pdat.cb128)
p1   <- create.bar.plots(pdat,show.legend = FALSE)
pdat <- rbind(pdat.b1,pdat.b8,pdat.b128)
p2   <- create.bar.plots(pdat)
plot_grid(p1,p2,nrow = 1,rel_widths = c(7,4))
```

>>>>

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
theme_set(theme_cowplot())
```

@@

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x <- rpois(n,mu.s)
p1 <- create.signal.plot(t,x,mu.s)
print(p1)
```

@@

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x <- rpois(n,mu.ang)
p2 <- create.signal.plot(t,x,mu.ang)
print(p2)
```

@@

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x <- rpois(n,mu.hs)
p3 <- create.signal.plot(t,x,mu.hs)
print(p3)
```

@@

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x <- rpois(n,mu.bur)
p4 <- create.signal.plot(t,x,mu.bur)
print(p4)
```

@@

```{r plot-cb-function, fig.height=2.5, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x <- rpois(n,mu.cb)
p5 <- create.signal.plot(t,x,mu.cb)
print(p5)
```

@@

```{r plot-bumps-function, fig.height=2.5, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x <- rpois(n,mu.b)
p6 <- create.signal.plot(t,x,mu.b)
print(p6)
```

@@

pdat <- rbind(pdat.s1,pdat.s8,pdat.s128,
              pdat.ang1,pdat.ang8,pdat.ang128,
              pdat.hs1,pdat.hs8,pdat.hs128,
              pdat.bur1,pdat.bur8,pdat.bur128,
              pdat.cb1,pdat.cb8,pdat.cb128)
pA   <- create.bar.plots(pdat,show.legend = FALSE)
pdat <- rbind(pdat.b1,pdat.b8,pdat.b128)
pB   <- create.bar.plots(pdat)
plot_grid(pA,pB,nrow = 1,rel_widths = c(7,4))
```
